Digital History in Finland, 1488-1828

### 2016-07-04 inst/examples/manuscript-krakow.Rmd
ok

print(paste(sel, collapse = ";"))

@@

# TITLE COUNT
theme_set(theme_bw(20))
p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
       geom_point(aes(col = language, shape = language), size = 5) +
       geom_line(aes(col = language, shape = language)) +       
       xlab("Publication year") +
       ylab("Title count (n)") +
       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
print(p)

# PAPER CONSUMPTION
theme_set(theme_bw(20))
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(col = language, shape = language), size = 5) +
       geom_line(aes(col = language, shape = language)) +       
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Languages (", catalogue, ")", sep = ""))
print(p)
}
```

>>>>

@@

# TITLE COUNT
theme_set(theme_bw(20))
p <- ggplot(df, aes(x = publication_decade, y = n, group = language)) +
       geom_point(aes(col = language, shape = language), size = 5) +
       geom_line(aes(col = language, shape = language)) +       
       xlab("Publication year") +
       ylab("Title count (n)") +
       ggtitle(paste("Title count (", print(paste(sel, collapse = ";")), ")", sep = ""))
print(p)

# PAPER CONSUMPTION
theme_set(theme_bw(20))
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(col = language, shape = language), size = 5) +
       geom_line(aes(col = language, shape = language)) +       
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Paper (", print(paste(sel, collapse = ";")), ")", sep = ""))
print(p)
}
```
